%% Se lect the dissertation mode on
% See the documentation for more information about the available class options
% If you give option 'draft' or 'draft*', the draft mode is set on
\documentclass[dissertation,math,vertlayout]{aaltoseries}
\usepackage[utf8]{inputenc}

% TODO: remove
\usepackage{todonotes}

\usepackage{xspace} % for \setype
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{glossaries}

\usepackage{hyperref}
\hypersetup{
	breaklinks,
    pdfpagemode={UseOutlines},
    bookmarksopen,
    pdfstartview={FitH},
    colorlinks,
    linkcolor={blue},
    citecolor={red},
    urlcolor={blue}
}

% Set the document languages
\usepackage[finnish,english]{babel}
\usepackage{amsmath,amssymb,amsthm}
\interdisplaylinepenalty=2500 % after amsmath to restore bad page breaks in the middle of equations
 % Adjust math line spacing
\renewcommand*{\arraystretch}{1.2} % for array/matrix environments
\setlength{\jot}{8pt} % for split environment

\usepackage{listings}
\usepackage[indentfirst=false,vskip=3mm]{quoting}

\newcommand{\textbfit}[1]{{\textbf{\textit{#1}}\xspace}}
\newcommand{\setype}[1]{{\texttt{#1}\xspace}}
\newcommand{\intel}[0]{Intel{}\xspace}

% The author of the dissertation
\author{Elena Reshetova}
% The title of the thesis
\title{Mobile and Embedded Platform Security}

\makeglossaries

\begin{document}

%% The abstract of the dissertation in English
% Use this command!
\draftabstract{TBD}


%% Preface
% If you write this somewhere else than in Helsinki, use the optional location.
\begin{preface}[Sipoo]
TBD
\end{preface}

%% Table of contents of the dissertation
\clearpage
\tableofcontents

% To be defined before generating list of publications. Leave off if no acknowledgement
%\languagecheck{the Institute of Language Checks}

\listofpublications

\chapter*{Other Publications}%
\addcontentsline{toc}{chapter}{Other Publications}%
The following publications are not included in this thesis. However Publication VII is an extended version of Publication I and therefore also referred to in this thesis.
\begin{enumerate}%
		\setcounter{enumi}{6}
		\renewcommand{\labelenumi}{\bfseries\Roman{enumi}}%
			\item Asokan, N. and Davi, Lucas and Dmitrienko, Alexandra and Heuser, Stephan and Kostiainen, Kari and Reshetova, Elena and Sadeghi, Ahmad-Reza. Mobile Platform Security, Synthesis Lectures on Information Security, Privacy, and Trust, \textit{Morgan \& Claypool Publishers}, December 2013
\end{enumerate}%
		
\clearpage

%Terms
\newglossaryentry{mac}{name=MAC, description={Mandatory Access Control}}

\printglossaries

%% Add list of abbreviations, list of symbols, etc., using your preferred package/method.

\chapter{Introduction}
\label{sec:introduction}
\input{chapters/introduction}

\todo[inline]{Unify style and colors of all figures through dissertation}
                

\chapter{Mobile and Embedded Platform Security}
\label{sec:plat-sec}
\input{chapters/plat-sec} 


\chapter{Process isolation and access control policies}
\label{sec:ac-policies}
\input{chapters/ac-policies} 

\chapter{OS Kernel Hardening}
\label{sec:kernel-hardening}
\input{chapters/kernel-hardening} 

\chapter{Future Outlook and Conclusions}
\label{sec:discussion}
\input{chapters/discussion} 

\renewcommand{\bibname}{References}
\bibliographystyle{plain} % Change as required
\bibliography{references}  % remember to edit the file name


% Errata list, if you have errors in the publications.
%\errata


\addpublication[conference]{Kostiainen, Kari and Reshetova, Elena and Ekberg, Jan-Erik and Asokan, N.}{Old, new, borrowed, blue: a perspective on the evolution of mobile platform security architectures}{Proceedings of the First ACM Conference on Data and Application Security and Privacy}{San Antonio, USA, pages 13--24}{February}{2011}{ACM}{c1}
% Add the dissertation author's contribution to that publication (the order can be interchanged with \adderrata).
\addcontribution{This publication presents a survey of four mobile platform security architectures, as well as description of the common hardware-based security mechanisms. The author contributed to this publication by surveying two of these architectures and helped identifying the common patterns in their design. The author also contributed to the writing of this publication together with other authors.}
% Add the errata of the publication, remove if there are none (the order can be interchanged with \addauthorscontribution).
%\adderrata{This is wrong}
% Add the publication pdf file, the filename is the parameter (must be the last).
\addpublicationpdf{publications/P1.pdf}

\addpublication[conference]{Reshetova, Elena and Bonazzi, Filippo and Nyman, Thomas and Borgaonkar, Ravishankar and Asokan, N}{Characterizing SEAndroid Policies in the Wild}{2nd International Conference on Information Systems Security and Privacy}{Rome, Italy}{February}{2016}{ICISSP}{c2}
% Add the dissertation author's contribution to that publication.
\addcontribution{The author's contribution to this publication includes leading the analysis of collected SEAndroid policies, identifying the common OEMs pitfalls and problems, as well as developing ideas on the required tools to help OEMs to create better SEAndroid policies. The author also contributed to the writing of this publication together with other authors.}
% No errata
% Add the publication pdf file, the filename is the parameter.
\addpublicationpdf{publications/P2.pdf}


\addpublication[conference]{Reshetova, Elena and Bonazzi, Filippo and and Asokan, N}{SELint: an SEAndroid policy analysis tool}{3nd International Conference on Information Systems Security and Privacy}{Porto, Portugal}{February}{2017}{ICISSP}{c3}
% Add the dissertation author's contribution to that publication.
\addcontribution{The author contributed to this publication by leading the design of SELint tool, including gathering OEM requirements for it and understanding OEM policy development flows. The tool itself was implemented by Filippo Bonazzi. The author also led the writing of this publication.}
% No errata
% Add the publication pdf file, the filename is the parameter.
\addpublicationpdf{publications/P3.pdf}

\addpublication[conference]{Reshetova, Elena and Karhunen, Janne and Nyman, Thomas and Asokan, N}{Security of OS-Level Virtualization Technologies}{19th Nordic conference on Secure IT Systems}{Tromsø, Norway, pages 77-93}{October}{2014}{Springer International Publishing Switzerland 2014}{c4}
% Add the dissertation author's contribution to that publication.
\addcontribution{The author's contribution to this publication consists of defining the system and attacker models for the OS-level virtualization, as well as identifying its security requirements. The author also contributed to the comparison of existing OS-level virtualization solutions by surveying four of them, as well as helped in identifying the current status and shortcomings of the mainline Linux OS-level virtualization mechanism, i.e. \textit{kernel namespaces}.}
% No errata
% Add the publication pdf file, the filename is the parameter.
\addpublicationpdf{publications/P4.pdf}


\addpublication[conference]{Reshetova, Elena and Bonazzi, Filippo and Asokan, N}{Randomization Can't Stop BPF JIT Spray}{Network and System Security: 11th International Conference}{Helsinki, Finland, pages 233-247}{August}{2017}{Springer International Publishing}{c5}
% Add the dissertation author's contribution to that publication.
\addcontribution{The author did the analysis of the BPF JIT implementation and developed initial versions of both BPF JIT Spray attack approaches described in this publication. Author also participated in the attack evaluation efforts, as well as led the writing of the publication.}
% No errata
% Add the publication pdf file, the filename is the parameter.
\addpublicationpdf{publications/P5.pdf}


\addpublication[submitted]{Reshetova, Elena and Liljestrand, Hans and Paverd, Andrew and Asokan, N}{Towards Linux Kernel Memory Safety}{Journal TBD}{Location, pages, and other detailed information}{Month}{2018}{Published TBD}{c6}
% Add the dissertation author's contribution to that publication.
\addcontribution{The author's contribution to this publication includes working on the design, implementation and mainline Linux kernel contribution of the reference counter overflow protection mechanism. In addition author also worked on design of \textit{MPXK}, a spatial memory errors protection solution for the Linux kernel, presented in this publication. The implementation of MPXK was done by Hans Liljestrand. The author also contributed to the writing of this publication together with other authors.}
% No errata
% Add the publication pdf file, the filename is the parameter.
\addpublicationpdf{publications/P6.pdf}

\end{document}
